---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# offensiveR

The goal of offensiveR is to help check for misspelled that are not caught with normal spells checking because they are misspelled to an offensive word.  

Examples include:

* mass - ass
* but - butt
* assess - asses

This package crosscheck with a quite large list of words, many of which will not be found offensive to most, but it deemed a good starting point.

## Installation

You can install offensiveR from github with:

```{r gh-installation, eval = FALSE}
# install.packages("offensiveR")
devtools::install_github("EmilHvitfeldt/offensiveR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(offensiveR)
```

The package consists of two major functions. `offensive_check_files()` and `offensive_check_string()`. `offensive_check_files()` takes a vector of paths to files, and returns the possible offensive words and their location.

```{r}
offensive_check_files(c("README.Rmd"))
```

`offensive_check_string()` takes a character string as input, and can be quite handy if you need to check an email you are about to send.

```{r}
text <- "Dear Jones
         
         The task you ask me will we hard to do since the ass is hard to 
         measure in motion. It will be hard to asses, butt I think we will 
         manage.

         Regards Tom"


offensive_check_string(text)
```

All functions comes with the two arguments `words_add` and `words_ignore` to add words to look for, and words to ignore respectively.

## Thanks

This package would not have been made have I not gotten the Idea from this tweet

<blockquote class="twitter-tweet" data-lang="da"><p lang="en" dir="ltr">Despite having sent out emails and surveys to 20K+ people countless times before, I still get nervous each time I have to do it 😂</p>&mdash; Jesse Maegan (@kierisi) <a href="https://twitter.com/kierisi/status/924292995435978752?ref_src=twsrc%5Etfw">28. oktober 2017</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>


and the [spelling](https://github.com/ropensci/spelling) package which much of the package is based on.
